SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-11 frontrunning/Latex/sections/paper.tex
Blocked! will wrap up ENS tmr.

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in a bid, but not the bid amount. Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name: \texttt{startAuctionsAndBid()}. This method leaks the hash of the domain and the initial bid amount in the auction. Original names can be guessed from the hashes (\eg rainbow tables, used in ENS Twitter bot) or people can bid on domains even though they do not know what they are because of speculation on its value.

Users are allowed to bid for 3 days before the 48-hour reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount . Also note that if two bidders bid the same price, the first to reveal wins it.

Two strategies: (1) Attacker knows the domain name, then he makes sure he is first to reveal. (2) Attacker is speculating, so he waits to see other reveal, then insert myself with the information from the other reveal. (3) If my amount is bigger, I see other reveal and then reveal.

@@

A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction~\cite{ENSHandlingFrontRunningDiscussion}. The auction model is similar to open auctions in \ref{sec:cryptogames}.

>>>>

The final category in Table~\ref{tab:top25DApps} is name services, which are primarily aimed at disintermediating central parties involved in web domain registration (\eg ICAAN and registrars) and resolution (\eg DNS). For simple name services (such as some academic work like Ghazal~\cite{moosavighazal}), domains purchases are transactions and front-runners can displace other users attempting to register domains. This parallels front-running attacks seen in regular (non-blockchain) domain registration~\cite{sac022en33:online}. \textsf{Ethereum Name Service (ENS)}~\cite{ensEIP} is the most active naming service on Ethereum. Instead of allowing new \texttt{.eth} domain names to be purchased directly, they are put up for a sealed bid auction which seals the domain name in a bid, but not the bid amount. Most implementations use the more user friendly but less confidential method for starting and bidding on a domain name: \texttt{startAuctionsAndBid()}. This method leaks the hash of the domain and the initial bid amount in the auction. Original names can be guessed from the hashes (\eg rainbow tables, used in ENS Twitter bot\footnote{\url{https://twitter.com/ensbot}}) or people can bid on domains even though they do not know what they are because of speculation on its value.

Users are allowed to bid for 3 days before the 48-hour reveal phase begins (see ~\ref{sec:comm}), in which all bidders (winners and losers) must send a transaction to reveal their bids for a specific domain or sacrifice their bid amount . Also note that if two bidders bid the same price, the first to reveal wins it~\cite{ENSHandlingFrontRunningDiscussion}. Combined with the leaked information, this introduces a race condition which could be mitigated if bidding time was taken into effect instead of solely reveal time.

Two strategies: (1) Attacker knows the domain name, then he makes sure he is first to reveal. (2) Attacker is speculating, which he will bid with a slightly higher value %so he waits to see other reveal, then insert myself with the information from the other reveal. (3) If my amount is bigger, I see other reveal and then reveal.

Sealed bids could easily be identified from the recent transactions --> depends on the anonymity set

@@

%A front-runner using the leaked information can bid with the same amount and reveal prior to the original bidder to win the auction.

Also using the leaked information, the front-running attack vector mimics the traditional domain front-running attacks. The auction model is similar to open auctions in \ref{sec:cryptogames}.
